---
title: "Homework 3 - Answer Key"
author: "Melinda Higgins & Vicki Hertzberg"
date: "February 21, 2018"
output:
  pdf_document: default
  html_document: default
  word_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1 - Document that you have installed `dada2` and `phyloseq`, as well as `shortread` and `ggplot2`.

Yes, I successfull installed these packages. Here is proof that `dada2` is working.

NOTE, the following versions should have been installed:

* `dada2` version 1.6.x - see [https://www.bioconductor.org/packages/release/bioc/html/dada2.html](https://www.bioconductor.org/packages/release/bioc/html/dada2.html)
* `ggplot2` version 2.2.x - see [https://cran.r-project.org/web/packages/ggplot2/index.html](https://cran.r-project.org/web/packages/ggplot2/index.html)
* `ShortRead` version 1.36.x - see [https://www.bioconductor.org/packages/release/bioc/html/ShortRead.html](https://www.bioconductor.org/packages/release/bioc/html/ShortRead.html)
* `phyloseq` version 1.22.x - see [https://www.bioconductor.org/packages/release/bioc/html/phyloseq.html](https://www.bioconductor.org/packages/release/bioc/html/phyloseq.html)

```{r}
library(dada2); packageVersion("dada2")
library(ggplot2); packageVersion("ggplot2")
library(ShortRead); packageVersion("ShortRead")
library(phyloseq); packageVersion("phyloseq")
```

## Problem 2 - Please document that you have downloaded the THREE additional files:

* the fastq files from the Mothur MiseqSOP walkthrough
* silva_nr_v132_train_set.fa.gz
* silva_species_assignment_v132.fa.gz

```{r}
# the ~ should work on a Mac
# path <- "~/MiSeq_SOP"

# if you are on a Windows OS computer (like me), use 
# . instead of ~
path <- "./MiSeq_SOP"

# list the files in the
# /MiSeq_SOP directory
fns <- list.files(path)
fns
```


